Data Preparation

### 2019-01-11 Data Preparation.Rmd
specifies types of columns

```{r import d_transcript, cache = TRUE}
d_transcript <- rbind(read_csv("Raw Grades/grades1.csv", col_types = cols()),
                      read_csv("Raw Grades/grades2.csv", col_types = cols()))
```

>>>>

```{r import d_transcript, cache = TRUE}
d_transcript <- rbind(
  read_csv("Raw Grades/grades1.csv", 
           col_types = cols(`Program (Abbreviation)`=col_character(), `Appraisal Status`= col_character(), `Module Booking Reason (Description)`= col_character(), `Object name` = col_character(), `Start date` = col_character(),`End Date` = col_character()
                              )
           ),
  read_csv("Raw Grades/grades2.csv", 
           col_types = cols(`Program (Abbreviation)`=col_character(), `Appraisal Status`= col_character(), `Module Booking Reason (Description)`= col_character(), `Object name` = col_character(), `Start date` = col_character(), `End Date` = col_character()
           )
           )
  )
```
